Depression and suicidality as costly signals of need

### 2021-04-04 Paper.rmd
Resolved merge conflict

The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression and, (5) a suicide attempt.

@@

>>>>

The sole treatment in this study was the signal participants saw, with these signals including: (1) a verbal request without additional signaling, (2) crying, (3) mild-depression, (4) depression, and (5) a suicide attempt.

@@

## Lessons learned from a pilot study

The current study is a refinement of a vignette-based pilot study (N=`r nrow(signalingdata2018b)`) with very similar signals and outcomes. In the pilot study, there was a single vignette in which an imagined sister claims her child needs an expensive emergency medical procedure, and asks for a very large loan. We learned five major lessons from the pilot study that influenced the design of the current study. First, as predicted, belief in the sister's need was low in the *Verbal request* condition and high in the *Depression* condition, giving us confidence to continue this research (see Figure \@ref(fig:piloteffects)). Second, to rule out that believability and willingness to help were simply artifacts of the sister's psychiatric distress, we included a "signaling" condition in which the sister exhibited schizophrenic symptoms. As predicted, believability and willingness to help in this condition were dramatically lower than in any other condition, ruling out this alternative explanation. We therefore did not replicate the schizophrenic condition in the current study. Third, baseline (T1) believability was very high (mean = `r signif(pilot_results$meanT1belief, 2)`, median = `r signif(pilot_results$medianT1belief, 2)` on a 0-100 point scale), leaving little scope for signals to increase believability. In the current study we therefore endeavored to provide details in the vignettes that would undermine the victim's believability at baseline. Fourth, contrary to our hypothesis, the *Suicide threat* and *Suicide attempt* signals reduced believability relative to *Depression*. We surmised that the sister's adversity -- a sick child -- was not sufficient to justify a suicide attempt, thus undermining her believability. In the current study the signaler herself is therefore the victim, and the forms of adversity -- physical and sexual assault and thwarted and forced marriage -- are those that are frequently associated with suicidality. Fifth, the content of the vignette matters, so instead of a single vignette we decided to use four different vignettes to help determine the extent to which signaling effects were sensitive to seemingly irrelevant details of the vignettes.
